---
title: "Readme"
output: github_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(wizaRd)
```

wizaRd
=====

A list of D&D 5e edition and some functions to fiddle with them.

Spell data taken from https://github.com/thebombzen/grimoire, originally https://github.com/ephe/grimoire/.

Installation
----------

```
devtools::install_github('oganm/diceSyntax')
devtools::install_github('oganm/wizaRd')

```

Usage
-----

The package includes a list that include all 5e spells called `spells`. Each element of this list is a list that holds different attributes of the spells.

```{r}
spells$`Acid Splash` %>% ls

spells$`Acid Splash`$components
```

Individual spells have a special print function (`print.spell`). When a spell is called the text for the spell is printed and any dice roll found to be associated with the spell based on the text is rolled

```{r}
spells$Immolation
```

The `spells` object also has a special print function (`print.spellList`).

```{r}
head(spells)
```

A few utility functions exist to create subset `spellList`s
```{r}
spells %>% filterSpells(level=c(0,1),class= 'bard',sources='PHB',school='evocation')

makeBook(level=3)
```
